On Secure Delegation of SampBQP with a Classical Client

### 2020-02-02 qpip.tex
Remove extra empty section
Make flow of blind then fully classical consistent
Use protocol env for QPIP1 SampBQP

\section{Our Delegation Protocols}

@@

@@

\floatname{algorithm}{Protocol}
\begin{algorithm}
	\caption{ $\QPIP_1$ protocol for $\SampBQP$}
	\label{ProtoQPIP1}
	\begin{algorithmic}[1]
		\Procedure{QPIP1}{$C, x, c$}
		\State Let $\varepsilon=T^{-c}$
		\State Let $m$ be large enough so that $\frac{1}{2^m}$ is negligible in $\varepsilon$
		\State Let $n$ be large enough so both $P\left[Bin(n, \frac{1}{2}-2\varepsilon)\geq\left(\frac{1}{2}-\varepsilon\right)n\right]$ and $P\left[Bin(n, \frac{1}{2})\leq\left(\frac{1}{2}-\varepsilon\right)n\right]$ are negligible in $\varepsilon$ by Chernoff bound
		\State Let $N$ be large enough so that $\sqrt{\frac{2(m+n)^2\ln\abs{A}}{N-(m+n)}}<\varepsilon$, where $\abs{A}$ is the number of qubits in $\ket{\psi_{C(x)}}$.

		\State The honest prover sends $N$ identical copies of $\ket{\psi_{C'(x)}}$, where $C'$ is $C$ padded with identities as mentioned in \hyperref[idpadding]{Observation~\ref*{idpadding}}
		\State The verifier randomly picks $m$ copies for outputting and $n$ copies for checking
		\State $c\gets0$
		\State $y\gets\bot$
		\For{$i\gets1, N$}
			\If{Copy is for checking}
			\State The verifier runs \autoref{AlgGroundStateCheck} as described by \hyperref[ProtoGroundStateCheck]{Observation~\ref*{ProtoGroundStateCheck}}.
			\If{Test passes}
				$c\gets c+1$
			\EndIf
			\ElsIf{Copy is for outputting}
			\State The verifier measures the copy in standard basis
			\If{measurement result of the clock register $\geq\frac{T}{2}$}
				\If{$y=\bot$}
					\State $y\gets$ measurement result of the data register
				\EndIf
			\EndIf
			\Else
			\State The verifier measures the entire register in standard basis
			\EndIf
		\EndFor
		\If{$\frac{c}{n}\geq\frac{1}{2}-\varepsilon$}
		\If{$y\ne\bot$}
		\State output $y$
		\Else
		\State Reject
		\EndIf
		\Else
		\State Reject
		\EndIf
		\EndProcedure
	\end{algorithmic}
\end{algorithm}

>>>>

@@

\Ethan{Remark on amplification and doing this qubit-by-qubit by last section. Do some general story-telling.}

@@

\begin{protocol}{$\QPIP_1$ protocol for $\SampBQP$}
	\label{ProtoQPIP1}
	Let $\varepsilon=T^{-c}$. \Ethan{Try setting up this $\varepsilon$ more intuitively}
	Let $m$ be large enough so that $\frac{1}{2^m}$ is negligible in $\varepsilon$
	Let $n$ be large enough so both $P\left[Bin(n, \frac{1}{2}-2\varepsilon)\geq\left(\frac{1}{2}-\varepsilon\right)n\right]$ and $P\left[Bin(n, \frac{1}{2})\leq\left(\frac{1}{2}-\varepsilon\right)n\right]$ are negligible in $\varepsilon$ by Chernoff bound
	Let $N$ be large enough so that $\sqrt{\frac{2(m+n)^2\ln\abs{A}}{N-(m+n)}}<\varepsilon$, where $\abs{A}$ is the number of qubits in $\ket{\psi_{C(x)}}$.
	\begin{enumerate}
		\item The honest prover sends $N$ identical copies of $\ket{\psi_{C'(x)}}$, where $C'$ is $C$ padded with identities as mentioned in \hyperref[idpadding]{Observation~\ref*{idpadding}}
		\item The verifier randomly picks $m$ copies for outputting and $n$ copies for checking
		\item $c\gets0$
		\item $y\gets\bot$
		\item For $i$ from $1$ to $N$:
		\begin{enumerate}
			\item If the $i$-th register is for checking:
			\begin{enumerate}
				\item The verifier runs \autoref{AlgGroundStateCheck} as described by \hyperref[ProtoGroundStateCheck]{Observation~\ref*{ProtoGroundStateCheck}}.
				\item If the test passes, increment counter $c$.
			\end{enumerate}
			\item If the register is for outputting:
			\begin{enumerate}
				\item The verifier measures the copy in standard basis
				\item If the measurement result of the clock register $\geq\frac{T}{2}$ and $y=\bot$, then set $y$ as the measurement result of the data register.
			\end{enumerate}
			\item Otherwise, just measure the entire register in standard basis and discard it.
		\end{enumerate}
		\item If $\frac{c}{n}\geq\frac{1}{2}-\varepsilon$:
		\begin{enumerate}
			\item If $y\ne\bot$ then output $y$
			\item Otherwise, reject.
		\end{enumerate}
		\item Otherwise, reject.
	\end{enumerate}
\end{protocol}
